Emissions and Perceptions of Climate Change

### 2022-11-29 Code/Drafts/Draft_2_GHG_Emissions_&_Perceptions_of_Climate_Change.Rmd
Enough to make a professor swear

Reading in the Data
```{r}
emissions<-read.csv(here("Data for the Code", "Corrected_Data_sets", "emissions_corrected_US_Denmark.csv"))
```

Lets turn the date column into date data using the lubridate package.  
To do that we need to put in the day and the month using paste.

@@

Below works fine, but just so you are aware, it is base R and not lubridate.

@@

@@

>>>>

Reading in the Data
```{r}
emissions<-read.csv(here("Data for the Code", "Corrected_Data_sets", "emissions_corrected_US_Denmark.csv"), stringsAsFactors = TRUE)
```

Lets turn the date column into date data using base R.  
To do that we need to put in the day and the month using paste.

@@

@@

```{r}
emissions$rate<-NA
denmark_rate<- emissions %>% filter(country=="Denmark")
den_rate<- diff(denmark_rate$emissions)
denmark_rate$rate[2:30]<-den_rate
denmark_rate<-denmark_rate[2:30,]

emissions$rate<-NA
usa_rate<- emissions %>% filter(country=="United States")
us_rate<- diff(usa_rate$emissions)
usa_rate$rate[2:30]<-us_rate
usa_rate<-usa_rate[2:30,]

emissions_rate<- rbind(usa_rate, denmark_rate)
emissions_rate_2010<- emissions_rate %>% filter(emissions_rate$year>="2005-01-01")

```{r}
ggplot(emissions_rate, aes(year, rate, colour= country, group=country)) +  geom_line() +
  geom_point(aes(colour=country))+ theme_bw() #colour colors by country, and group tells R to group the points by country so geom_line will draw lines connecting the data by country.
```

```{r}
t.test(rate~country, data=emissions_rate, paired=TRUE)
#complete.cases means just use the ones without NAs
```

```{r}
t.test(rate~country, data=emissions_rate_2010, paired=TRUE)
```

@@

???______
1101 people answered in Denmark
3096 answered in United States

```{r}
beliefs <- beliefs %>% group_by(Country)

dumb_way<- c(1101,3096,1101,3096,1101,3096,1101,3096,1101,3096,1101,3096)
beliefs<- cbind(beliefs, dumb_way)
beliefs<-beliefs %>% rename(num_people=...5)

beliefs<- beliefs %>% group_by(Country, response) %>%  mutate(total=(Number/100)*num_people)

beliefs$total<- round(beliefs$total, digits=0)

test<- beliefs %>% select(response, Country, total)
```

???? The chi-squared below did not work!!!
Chi-squared
```{r}
beliefs_matrix<-xtabs(total~Country + response, data=test)
beliefs_matrix
beliefs_df<- as.data.frame(beliefs_matrix)
beliefs_df<- beliefs_df %>% filter(Freq>0)
beliefs_matrix_real<- xtabs(Freq~Country+response, data=beliefs_df)
beliefs_matrix_real
chisq.test(beliefs_matrix)

```
???___

```{r}
vector_Den<- c(585,57,419,19,16,1)
vector_US<-c(1295,473,1073,86,161,7)
matrix<- as.matrix(rbind(vector_Den, vector_US))
chisq.test(matrix)
